Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
small change to mfcc interpretation (ASSR)

>>>>

The same observations are made for the MFCCs for $k\leq5$. However for a rank $k$ greater than $5$, all the \emph{ob} approaches perform equivalently. This may be due to the fact that, at some point, the MFCCs fail to dissociate the discriminative events of a scene from the non-informative ones, thus making the cluster selection/weighting step useless.
